Visuals

### 2025-02-20 scripts/visuals.Rmd
update paper link

```{r setup, include=FALSE}
library(tidyverse)
library(jsonlite)
library(stringr)
library(ggpubr)
library(tidyboot)
library(readxl)
library(brms)
library(ggthemes)
library(writexl)
library(ggdist)
library(sf)
library(grid)
library(geomtextpath)
library(ggridges)
```

@@

```{r}
pac<- data%>%
  group_by(subjID)%>%
  mutate(n = n())%>%
  filter(n == 379)%>%
  select(-n)%>%
  group_by(subjID, age, word_type)%>%
  #group_by(subjID, age)%>%
  summarise(mean = mean(score))%>%
  ggplot(aes(x = age, y = mean, col = word_type))+
  labs(x = "Child age", y = "Proportion response yes")+
  geom_point(pch = 1, alpha = 0.5)+
  geom_smooth(method = "loess", alpha = .2)+
  #stat_cor(label.y.npc = "bottom",label.x.npc = 0.8, show.legend = FALSE, aes(label = paste(..r.label..)), cor.coef.name = "r")+
  scale_color_colorblind(name = "Word type", guide = guide_legend(reverse = TRUE))+
  scale_fill_colorblind(name = "Word type", guide = guide_legend(reverse = TRUE))+
  #facet_grid(~word_type)+
  theme_bw()
```
```{r}
ggarrange(wtd, wac,pac, nrow = 1, labels = c("A","B", "C"), widths = c(0.7,1,1.2))
```
```{r}
ggsave("../graphs/fig2.png", width = 12, height = 3, scale = 1.25, bg = "white")
```

@@

```{r}
ggsave("../graphs/fig3.png", height = 3.5, width = 12, scale = 1.25, bg = "white")
```

@@

```{r}
ggsave("../graphs/fig4.png", height = 5, width = 10, scale = 1.25, bg = "white")
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(jsonlite)
library(stringr)
library(ggpubr)
library(tidyboot)
library(readxl)
library(brms)
library(ggthemes)
library(writexl)
library(ggdist)
library(sf)
library(grid)
library(geomtextpath)
library(ggridges)
library(cowplot)
```

@@

```{r}
pac<- data%>%
  group_by(subjID)%>%
  mutate(n = n())%>%
  filter(n == 379)%>%
  select(-n)%>%
  group_by(subjID, age, word_type)%>%
  #group_by(subjID, age)%>%
  summarise(mean = mean(score))%>%
  ggplot(aes(x = age, y = mean, col = word_type))+
  labs(x = "Child age", y = "Proportion response yes")+
  geom_point(pch = 1, alpha = 0.5)+
  geom_smooth(method = "loess", alpha = .2)+
  #stat_cor(label.y.npc = "bottom",label.x.npc = 0.8, show.legend = FALSE, aes(label = paste(..r.label..)), cor.coef.name = "r")+
  scale_color_colorblind(name = "Word type", guide = guide_legend(reverse = TRUE))+
  scale_fill_colorblind(name = "Word type", guide = guide_legend(reverse = TRUE))+
  #facet_grid(~word_type)+
  theme_bw()
```
```{r}
ggarrange(wtd, wac,pac, nrow = 1, labels = c("A","B", "C"), widths = c(0.7,1,1.2))
```
```{r}
ggsave("../graphs/fig2.png", width = 12, height = 3, scale = 1.25, bg = "white")
ggsave("../graphs/fig2.pdf", width = 12, height = 3, scale = 1.25, bg = "white")
```

@@

```{r}
ggsave("../graphs/fig3.png", height = 3.5, width = 12, scale = 1.25, bg = "white")
ggsave("../graphs/fig3.pdf", height = 3.5, width = 12, scale = 1.25, bg = "white")
```

@@

```{r}
ggsave("../graphs/fig4.png", height = 5, width = 10, scale = 1.25, bg = "white")
ggsave("../graphs/fig4.pdf", height = 5, width = 10, scale = 1.25, bg = "white")
```
